+-+-+-+-+-+-+
Title of Study: My Perfect Pokemon (Exploring Descriptive Statistics)
Author: Amber P. Giza
+-+-+-+-+-+-+

# Step 1: Importing and viewing the data
First off, I added the necessary imports for the purposes of viewing and aggregating the data
within the R file. This file wouldn't require as many functions to perform as the last study I
conducted, with regarding gun violence, but there were some imports that I had to utilize.

```{r}
install.packages("ggplot2")
install.packages("tinytex")
install.packages("rmarkdown", dep = TRUE)
install.packages("plotly")
install.packages("DescTools")
install.packages("dplyr")

library(ggplot2)
library(tinytex)
library(rmarkdown)
library(plotly)
library(DescTools)
library(dplyr)

PerfectPokemon <- read.csv("My_Perfects_PAST.csv", header = TRUE, sep = ",")
View(PerfectPokemon)
```

Next, I checked to see if there are any nulls in the data, even though I am the one
who made the data, from gathering Perfect Pokemon inside Pokemon GO. Thankfully, there 
are no nulls.

```{r}
# Any null data?
sum(is.na(PerfectPokemon))
# 0
```

Afterwards, I wanted to do the analysis for each of the four main factors in statistical data:
* Mean
* Median
* Mode
* Standard Deviation

First off, these are the means for the Heights and Weights columns:

```{r}
# Statistical information

# Mean for each numeric column:
# For Heights and Weights
print("Mean values for each numeric column:")
print("Mean Height") # 1.7049
mean(PerfectPokemon$Height)
print("-----------------------------")

# Mean Weight
print("Mean Height") # 93.7856
mean(PerfectPokemon$Weight)
```

Next, the median values for the Heights and Weights:

```{r}
# Median Height:
print("Median value for the Height column:") # 1.375
median(PerfectPokemon$Height)
print("-------------------------------")

# Median Weight:
print("Median value for the Weight column:") # 55.01
median(PerfectPokemon$Weight)
```

Both the median values are less than the mean values.
Next, we view the Mode (most occuring values). The height column 
has several occuring values, but the weight column has all unique
values:

```{r}
# Mode Height:
print("Most occuring value for the Height column (if applicable):") # several: 0.89, 1.01, 1.21, 1.3, 1.47, and 1.56 meters
Mode(PerfectPokemon$Height)
print("-------------------------------")

# Mode Weight: 
print("Most occuring value for the Weight column (if applicable):") # None
Mode(PerfectPokemon$Weight)
```

For the Standard deviation, it is higher than the median and mean for height,
as well as the weight being higher than the mean and median for that column:

```{r}
# Standard Deviation Height:
print("Standard Deviation of the Height column:") # 1.988 meters
SD(PerfectPokemon$Height)
print("-------------------------------")

# Standard Deviation Weight: 
print("Standard Deviation of the Weight column:") # 103.85115 kilograms
SD(PerfectPokemon$Weight)
```

Next, I made boxplots on the height and the weight. For both, they have 
large outliers that may have skewed the data, which explains the Standard
deviation being so high:

```{r, echo=FALSE}
# Attempt to create boxplot on Height:
boxplot(PerfectPokemon$Height, data = PerfectPokemon,
        main = "Heights of My Perfects",
        xlab = "Data",
        ylab = "Height in Meters")
```

```{r, echo=FALSE}
boxplot(PerfectPokemon$Weight, data = PerfectPokemon,
        main = "Weights of My Perfects",
        xlab = "Data",
        ylab = "Weight in Kilograms")
```

Lastly, I constructed a histogram that counted each Pokemon by generation.
For some Pokemon like Sandslash and Rapidash, even though I found their Alolan
forms and those technically count as both generations 1 and 7, I made them default
to generation 1 for most of the files, because those Pokemon were from the 1st
generation, originally. 

```{r, echo=FALSE}
# Constructing the histogram:
# By generation
hist(PerfectPokemon$Generation, xlab="Amount of My Perfect Pokemon By Generation", col = "red", border = "black")
```